Commit Rater

### 2015-09-22 presentations/paper/methodology.tex
Make analysis-possibilities a little clearer

On each level, it is furthermore possible to analyse either the results of all criteria checks or only the check/checks for one criterion. These six possibilities will be discussed below.

@@

\subsubsection{Above repository-level}
It may be of further interest to look at the averages of adherence to guidelines across multiple repos and thereby extrapolate some general statistics about usage of the guidelines in the Git community. But we did not concern ourselves with this level, since we found it to be unrelated to our research questions.

>>>>

These three possibilities will be discussed below. Additionally, on each level it is possible to analyse either the results of all criteria checks or only the check/checks for one criterion. This distinction will be made where applicable.

@@

\subsubsection{Above repository-level}
Additionally to the analysis-possibilities stated above, it may be of further interest to look at the averages of adherence to guidelines across multiple repos and thereby extrapolate some general statistics about usage of the guidelines in the Git community. But we did not concern ourselves with this level, since we found it to be unrelated to our research questions.
